\dftfe{} is a C++ code for materials modeling from first principles using Kohn-Sham density functional theory.
It is based on adaptive finite-element discretization that handles all-electron and pseudopotential calculations in the 
same framework, and incorporates scalable and efficient solvers for the solution of the Kohn-Sham equations. Importantly, \dftfe{} can handle general geometries and boundary conditions, including periodic, semi-periodic and non-periodic systems. \dftfe{} code builds on top of the deal.II library for everything 
that has to do with finite elements, geometries, meshes, etc., and, through deal.II on p4est for parallel adaptive mesh handling.

\subsection{Authors}
\label{sec:authors}
\dftfe{} is hosted by the \href{http://www-personal.umich.edu/~vikramg/}{Computational Materials Physics
group at University of Michigan}, with Vikram Gavini, Associate Professor of Mechanical Engineering and Materials Science and Engineering, as
the principal investigator broadly overseeing this effort. The code is maintained by a group of principal developers, 
who manage the architecture of the code and the core functionalities. Developers with
significant contributions to core functionalities and code architecture in the past who are 
no longer active principal developers, are listed under principal developers emeriti. 
A subset of the principal developers and mentors are administrators. Finally, all contributors who have
contributed to major parts of the DFT-FE code or sent important fixes and enhancements are listed
under contributors. All the underlying lists are in alphabetical order. 

\paragraph{Principal developers}
\begin{itemize}
	\item Sambit Das (University of Michigan, USA).
	\item Phani Motamarri (University of Michigan, USA).
\end{itemize}

\paragraph{Principal developers emeriti}
\begin{itemize}
	\item Krishnendu Ghosh (University of Michigan, USA).
	\item Shiva Rudraraju (University of Wisconsin Madison, USA).	
\end{itemize}

\paragraph{Contributors}
\begin{itemize}
	\item Sambit Das (University of Michigan, USA).
	\item Denis Davydov (University of Erlangen-Nuremberg, Germany).
	\item Krishnendu Ghosh (University of Michigan, USA).
	\item Phani Motamarri (University of Michigan, USA).
	\item Shiva Rudraraju (University of Wisconsin Madison, USA).
	\item Sukhan Parekh (University of Michigan, USA). 	
\end{itemize}

\paragraph{Mentors}
\begin{itemize}
	\item Vikram Gavini (University of Michigan, USA).
\end{itemize}

\subsection{Acknowledgments}
The development of \dftfe{} open source code relating to pseudopotential calculations has been funded in part by the Department of Energy Software Center for Predictive Integrated Structural Materials Science at University of Michigan, and the Toyota Research Institute. The development of \dftfe{} open source code relating to all-electron calculations has been funded by the Department of Energy Basic Energy Science. The methods and algorithms that have been implemented in \dftfe{} are outputs from research activities over many years that have been supported by the Army Research Office, Air Force Office of Scientific Research, Department of Energy Basic Energy Science, National Science Foundation and Toyota Research Institute. 

\subsection{Referencing \dftfe{}}
Please refer to \href{https://sites.google.com/umich.edu/dftfe/publications}{referencing  \dftfe{}} to properly cite the use of \dftfe{} in your scientific work.  { \color{red} \{link needs to be updated if webpage changes\}}
